---
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage[dvipsnames]{xcolor}
output: github_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Dr Nicholas J Clark
=============================
Postdoctoral Fellow - University of Queensland, School of Veterinary Science   
Gatton, Queensland, Australia - nicholas.j.clark1214@gmail.com - 0432420979  
[Homepage](http://nicholasjclark.weebly.com/) - [Github](https://github.com/nicholasjclark) - [Google Scholar](https://scholar.google.com.au/citations?hl=en&user=5bO9uxEAAAAJ&view_op=list_works&gmla=AJsN-F7bdYY9zcTVOHPEOVWZOJmCtgWpcxs_93x6Nxu1saXGdZjQLZ9byuM7Bdln9uk-HvNvAG1pThmdF6m_XgubeW0Q2sVTsjvpgou00G94hSHvb99iNTk) - [ResearchGate](https://www.researchgate.net/profile/Nicholas_Clark4)


## Career Summary
Flexible and engaging disease ecologist with experience studying the geographical and biotic determinants of pathogen transmission. Interested in developing computational phylogenetic tools and adapting techniques from statistical network theory to study how pathogens interact with their hosts across urbanisation gradients.

## Transferable Skills
* Strong communication skills: 25 publications in peer-reviewed journals; five presentations at international conferences 
* Broad field experience: supervised teams of field researchers in both terrestrial and marine habitats
* Extensive experience using script-based programming: proficient with frequentist and probabilistic statistical analyses; maintain two `R` packages for community ecology and landscape genetics research
* Aptitude for leadership: trained four postgraduate students in bioinformatics and statistical techniques
* Proven ability to obtain funding: $87000 external funding from domestic and international organisations
* Proficient programming with: `R`, `html`, `MATLAB`, `Markdown`, `git`

## Qualifications
**PhD**  
**Griffith University** (Supervisors: Dr Sonya Clegg, Dr Robert Adlard, Prof. Hamish McCallum)  
Thesis: *The distribution and diversity of avian malaria parasites in Australian and Southern Melanesian birds*
  
* Led field expeditions in diverse habitats on four islands in New Caledonia and across two Australian states
* Acquired extensive experience programming epidemiological analyses for multistructure datasets using both frequentist and Bayesian techniques
* Published ten peer-reviewed papers over four years, including six published chapters by submission of the thesis  

**GDipResMeth**  
**James Cook University** (Supervisors: Prof Garry Russ, Dr Lynne van Herwerden)
Thesis: *Connectivity of butterflyfishes: pairing molecular methods and field observations*

* Lead volunteer divers on two field trips to conduct marine abundance and habitat complexity surveys
* Developed laboratory skills to conduct high-throughput genetic analyses
* Obtained a high distinction in a Sampling and Experimental Design course and developed key programming skills to build hierarchical models

**BSc (honours)**  
**University of North Carolina at Wilmington**; North Carolina, USA

* Dean’s list for academic achievement in all semesters (GPA 4.0/4.0)

\pagebreak

## Professional Experience
**Postdoctoral Fellow (7/2016 - 09/21)**  
**University of Queensland**, School of Veterinary Science

* Leading multiple funded projects to investigate the spread of zoonotic pathogens at the human-wildlife interface
* Co-supervising two PhD students in disease ecology and quantitative genetics
* Developing novel statistical network tools to study biotic interactions and their influences on infection risk

**Research Assistant (1/2016 - 7/16)**  
**University of Queensland**, School of Veterinary Science (Adviser: Dr Steven Kopp)

* Conducted molecular research into population genetics of soil-transmitted helminth parasites
* Established protocols to develop next generation sequencing tools for cat fleas

**Technical Laboratory Officer (fill-in for maternity leave; 9/2015 - 11/15)**  
**Biosecurity Laboratory**, Queensland Dept. Agriculture and Fisheries (Adviser: Dr Les Barker)

* Improved workflow efficiency by preparing reagents for three diagnostic laboratories 
* Cultured in-house microbe strains and carried out quality control testing 

## Summary Citation Metrics
```{r echo=FALSE, fig.align='center', fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
source('scholar_summary.R')
scholar_summary(user = '5bO9uxEAAAAJ')
```

\pagebreak

## Publications in Review
Fountain-Jones, NM, **Clark, NJ**, Kinsley, AC, Carstensen, M, Johnson, TJ, Forester, J, Miller, E, Moore, S, Wolf, TM and Craft, ME. Microbial associations and spatial proximity predict North American moose (*Alces alces*) gastrointestinal community composition (1st submission 07/01/19)  
  
Proboste, T, Corvalan, P, **Clark, NJ**, Beyer, HL, Goldizen, AW and Seddon, JM. Commensal bacterial sharing is not predicted by host social association in kangaroos: implications for disease transmission networks (2nd revision 19/04/19)  
  
**Clark, NJ**, Drovetski, SV and Voelker, G. Avian malaria in the changing climate: denser vegetation and warmer winters increase parasite infection risk in Western Palearctic birds. (1st submission 08/04/19)  
  
**Clark, NJ**, Umulisa, I, Ruberanziza, E, Owada, K, Colley, DG, Ortu, G, Campbell, CH, Emmanuel, R, Lancaster, W, Mbonigaba, JB, Mbituyumuremyi, A, Fenwick, A, Soares Magalhaes, RJ and Turate, I. Mapping *Schistosoma mansoni* endemicity in Rwanda: a critical assessment of geographical disparities arising from Circulating Cathodic Antigen versus Kato-Katz diagnostics (1st submission 24/04/19)  

## Full Publication List
**2019**  
  
Wells, K, and **Clark, NJ**. Towards predicting host shifting by multi-host pathogens. *Trends in Parasitology* DOI: 10.1016/j.pt.2019.04.001 (IF: 7.929)  
  
Lawrence, AL, Webb, CE, **Clark, NJ**, Halajian, A, Mihalca, A, Miret, J, D'Amico, G, Brown, G, Kumsa, B, Modry, D, and Šlapeta, J. Out-of-Africa origins and global climatic distribution of the common cat flea, *Ctenocephalides felis*: the hitchhiker’s guide to world domination. *International Journal for Parasitology* DOI: 10.1016/j.ijpara.2019.01.001 (IF: 3.730)  
  
Fecchio, A, Wells, K, Bell, JA, Tkach, VV, Lutz, HL, Weckstein, JD, Clegg, SM, and **Clark, NJ**. Climate variation influences host specificity in avian malaria parasites. *Ecology Letters* DOI: 10.1111/ele.13215 (IF: 9.137)  
  
**2018**  
  
Wells, K, Gibson, D, and **Clark, NJ**. Global patterns in helminth host specificity: phylogenetic and functional diversity of regional host species pools matter. *Ecography* DOI: 10.1111/ecog.03886 (IF: 4.520)  
  

**Clark, NJ** and Soares Magalhães, RJ. Airborne geographical dispersal of Q Fever from livestock holdings to human communities: a systematic review and critical appraisal of evidence. *BMC Infectious Diseases* DOI: 10.1186/s12879-018-3135-4 (IF: 2.678)   
  
**Clark, NJ**, Wells, K, Lindberg, O. MRFcov: Markov Random Fields with additional covariates. `R` package version 1.0, https://github.com/nicholasjclark/MRFcov  
  
**Clark, NJ**, Wells, K, and Lindberg, O. Unravelling changing interspecific interactions across environmental gradients using Markov random fields. *Ecology* DOI: 10.1002/ecy.2221 (IF: 4.809)   
  
**Clark, NJ**. Phylogenetic uniqueness, not latitude, explains the diversity of avian blood parasite communities worldwide. *Global Ecology and Biogeography* DOI: 10.1111/geb.12741 (IF: 6.045)    
  
Wells, L, Gibson, DI, **Clark, NJ**, Ribas, A, Morand, S, McCallum, H. Global spread of helminth parasites at the human – domestic animal – wildlife interface. *Global Change Biology* DOI: 10.1111/gcb.14064 (IF: 8.502)   
  
**Clark, NJ**, Seddon, JM, Kyaw‐Tanner, M, Al-Alawneh, J, Harper, G, McDonagh, P, and Meers, J. Emergence of canine parvovirus subtype 2b (CPV-2b) infections in Australian dogs. *Infection, Genetics and Evolution* DOI: 10.1016/j.meegid.2017.12.013 (IF: 2.885)    
  
**Clark, NJ**, Seddon, JM, Šlapeta, J, and Wells, K. Parasite spread at the domestic animal - wildlife interface: anthropogenic habitat use, phylogeny and body mass drive risk of cat and dog flea (*Ctenocephalides* spp.) infestation in wild mammals. *Parasites & Vectors* DOI: 10.1186/s13071-017-2564-z (IF: 3.035)   
  

**2017**  
  
**Clark, NJ**, Clegg, SM, Sam, K, Goulding, W, Koane, B and Wells, K. Climate, host phylogeny and the connectivity of host communities govern regional parasite assembly. *Diversity and Distributions* DOI: 10.1111/ddi.12661 (IF: 4.391)    
  
**Clark, NJ** and Clegg, SM. Integrating phylogenetic and ecological distances reveals new insights into parasite host specificity. *Molecular Ecology* 26(11), 3074-3086 (IF: 6.086)        
  
McKee, J, **Clark, NJ**, Shapter, F and Simmons, G. A new look at the origins of Gibbon Ape Leukemia Virus. *Virus Genes* 53(2), 165-172 (IF: 1.431)      
  

**2016**  
  
**Clark, NJ**, Wells, K, Dimitrov, D and Clegg, SM. Co-infections and environmental conditions drive the distributions of blood parasites in wild birds. *Journal of Animal Ecology* 85(6), 1461-1470 (IF: 4.474)      
  
Aharon-Rotman, Y, Buchanan, KL, **Clark, NJ**, Klaassen, M and Buttemer, WA. Why fly the extra mile? Using stress biomarkers to assess wintering habitat quality in migratory shorebirds. *Oecologia* 182(2), 385-395 (IF: 3.130)    
  
Goulding, W, Adlard, RD, Clegg, SM and **Clark, NJ**. Molecular and morphological description of *Haemoproteus* (*Parahaemoproteus*) *bukaka* (species nova), a haemosporidian associated with the strictly Australo-Papuan host Subfamily Cracticinae. *Parasitology Research* 115, 3387-3400 (IF: 2.329)       
  
**Clark, NJ**, Clegg, SM and Klaassen, M. Migration strategy and pathogen risk: non‐breeding distribution drives malaria prevalence in migratory waders. *Oikos* 125(9), 1358-1368 (IF: 4.030)  

**2015**   
  
**Clark, NJ**, Ishtiaq, F, Olsson-Pons, S and Clegg, SM. Specialist enemies, generalist weapons and the potential spread of exotic pathogens: malaria parasites in a highly invasive bird. *International Journal for Parasitology* 45(14), 891-899 (IF: 3.730)       
  
Olsson-Pons, S, **Clark, NJ**, Ishtiaq, F and Clegg, SM. Differences in host species relationships and biogeographical influences produce contrasting patterns of prevalence, community composition and genetic structure in two genera of avian malaria parasites in southern Melanesia. *Journal of Animal Ecology* 84(4), 985-998 (IF: 4.474)   
  
**Clark, NJ**, Adlard, RD and Clegg, SM. Molecular and morphological characterization of *Haemoproteus* (*Parahaemoproteus*) *ptilotis*, a parasite infecting Australian honeyeaters (Meliphagidae), with remarks on prevalence and potential cryptic speciation. *Parasitology Research* 114(5), 1921-1928 (IF: 2.329)  
  
**Clark, NJ** and Clegg, SM. The influence of vagrant hosts and weather patterns on the colonisation and persistence of blood parasites in an island bird. *Journal of Biogeography* 42(4), 641-651 (IF: 4.248)  
  

**2014**  
  
**Clark, NJ**, Adlard, RD and Clegg, SM. First evidence of avian malaria in Capricorn Silvereyes (*Zosterops lateralis chlorocephalus*) on Heron Island. *The Sunbird* 44, 1-11  
  
**Clark, NJ**, Clegg, SM and Lima, MR. A review of global diversity in avian haemosporidians (Plasmodium and Haemoproteus: Haemosporida): new insights from molecular data. *International Journal for Parasitology* 44(5), 329-338 (IF: 3.730)    
  

**2012**  
  
**Clark, NJ** and Russ, GR. Ontogenetic shifts in the habitat associations of butterflyfishes (F. Chaetodontidae). *Environmental Biology of Fishes* 94, 579-590 (IF: 1.307)
  
\pagebreak

## Service and Discipline Involvement
**Service**  
  
* Active member of UQ School of Veterinary Science Research Committee
* Active member of UQ's Faculty of Science Equity, Diversity and Inclusion Committee
* Served as panel member to mark two UQ RHD theses
* Contributed to teaching and assignment design for three undergraduate courses at UQ
* Currently co-supervising two PhD students
* Student volunteer for the 2017 Australian Society for Parasitology International Conference

**Referee**  	
  
* *International Journal of Environmental Research and Public Health*
* *Malaria Journal*
* *Parasites & Vectors*
* *Infection, Genetics and Evolution*
* *Parasitology*
* *International Journal for Parasitology*
* *Evolutionary Applications*
* *Molecular Biology and Evolution*
* *Evolutionary Ecology*
* *Ecology Letters*
* *Journal of Biogeography*
* *Journal of Animal Ecology*

## Funding Support
**2019**  
  
**$AU35,090**: University of Queensland Early Career Researcher Grant (authored the proposal). TickAlert: development of an integrated early warning surveillance platform for tick paralysis
  
**2017**  
  
**$US18,400**: National Geographic Scientific Research Grant (co-authored the proposal). Tracing the spillover of fleas and paralysis ticks between wildlife and domestic pets in Australia  
  
**2015**  
  
**$AU4,975**: Birds Queensland Research Award (co-authored the proposal). The role of invasive birds as carriers of exotic pathogens; implications for co-occurring native birds  
  
**$AU3,125**: BirdLife Australia Stuart Leslie Bird Research Award (authored the proposal). Enemy release or novel weapons: malaria’s role in the spread of the invasive Indian Myna  
  
**2014**	 
  
**$AU2,000**: Griffith University Environmental fund for impactful publications  
  
**2013**  
  
**$US20,250**: National Geographic Scientific Research Grant (co-authored the proposal). Avian malaria in southern Melanesian birds  
  
**2012**  
  
**$AU3,750**: BirdLife Australia Stuart Leslie Bird Research Award (authored the proposal). Avian malaria lineage distribution, diversity and host specificity in southeast Queensland  
  
**$AU5,000**: Birds Queensland Research Award (authored the proposal). The prevalence, distribution and diversity of avian malaria parasites in southeast Queensland  
  
**$AU78,000**: Griffith University International Postgraduate Research Award

## Teaching Contributions
**2017**  
  
**University of Queensland**, Gatton Campus: Ecological and Disease Genetics (Course Coordinator)  
Undergraduate (3rd year Science), semester 1

* Planned learning objectives; wrote the electronic course profile (ECP) and all assignments
* Delivered flexible, interactive lectures and tutorials that were well-received by students
* Achieved overwhelmingly positive feedback on student evaluations, including scores of ‘Outstanding’ for teacher ratings
* SECaTs available at: VETS3042/Ecological and Disease Genetics/6720/23028

**University of Queensland**, Gatton Campus: Animal Breeding and Genetics (Course Coordinator)  
Undergraduate (Bachelor of Veterinary Medicine), semester 2

* Planned learning objectives; contributed to preparation of assignments and end of semester exam
* Independently lead theory-based genetics tutorials
* Nominated for a ‘Golden Speculum’ Best Lecturer award for 2017

**2016 - 17**  
  
**University of Queensland**, Gatton Campus: Molecular and Quantitative Plant Genetics; Molecular and Quantitative Animal Genetics (Lead tutor)  
Undergraduate (2nd year Science and 2nd year Agriculture), semester 2

* Independently lead laboratory and theory tutorials
* Marked assignments and liaised with course coordinators to enhance curriculums

**2015 - 17**  
  
**University of Queensland**, Gatton Campus: Animal Breeding and Molecular Genetics; Animal 
Pathogens and Immunity; Principles of Disease (Assistant tutor)  
Undergraduate (2nd year Veterinary Science), semesters 1 and 2

* Collaborated with fellow tutors to lead laboratory and theory tutorials
* Marked assignments

**2013**  
  
**Griffith University**, Gold Coast Campus: Ecology; Earth Sciences (Assistant tutor)  
Undergraduate (2nd year Science), semester 2

* Independently lead laboratory and theory tutorials

\pagebreak

## Mentoring And Research Training
**2017 - present**  
  
Co-supervising UQ PhD student (A. McGowan), studying population genomics of dugongs. This student is developing novel landscape genetics analyses and recently qualified for Faculty-level heats in the UQ Three Minute Thesis competition  
  
**2016 - present**  
  
Co-supervising UQ PhD student (T. Proboste), studying population genomics and host-parasite interactions in paralysis ticks. This student is adapting social network methods to study host-pathogen interactions, and has already presented at two conferences  
  
**2014 - 16** 	
  
Trained UQ PhD student (W. Goulding) in molecular techniques and aided project design, resulting in two collaborative papers (both in Parasitology Research) and one successful co-authored grant proposal (Birds Queensland; $AU4975)  
  
**2014**  
  
Trained Deakin University PhD student (Y. Aharon-Rotman) in Bayesian phylogenetic modelling, resulting in one collaborative paper (Oecologia)  
  
**2012 - 13**  
  
Trained Griffith University honour’s student (S. Olsson-Pons) in bioinformatics, resulting in two collaborative papers (Journal of Animal Ecology; International Journal for Parasitology) 

## Presentations and Societal Impacts
**2019**  
  
Oral presentation: Department of Wildlife and Fisheries Sciences, Texax A&M University, College Station, USA    
  
**2018**  
  
Oral presentation: Ecological Society of Australia Conference, Brisbane, Australia  
  
Oral presentation: Ministerio de Salud de Chile (MINSAL) Q Fever Delegation, Gatton, Australia  
  
**2017**  
  
Oral presentation: Australian Society for Parasitology Conference, Leura, Australia  
  

**2016**  
  
Research used to frame a Question Without Notice in NSW Parliament, from Shooters and Fishers Party MP to the Minister for Primary Industries  
  
Oral presentation: Griffith University Wildlife Disease Ecology Group, Brisbane, Australia  
  

**2015**  
  
Interviewed on ABC Radio National and ABC Radio Gold Coast regarding research on exotic malaria strains spread by invasive birds  
  
Interviewed for feature stories in the Australian Society for Parasitology quarterly newsletter and in Australian Birdlife regarding research on avian malaria in Australian birds  
  
Oral presentation: University of Queensland ARC Cavity Nesting Group, Brisbane, Australia  
  
Oral presentation: Evolutionary Ecology of Infectious Diseases Conference, Athens, USA  
  
Oral presentation: Griffith University Wildlife Disease Ecology Group, Brisbane, Australia  
  
Poster presentation: Wildlife Disease Association Conference, Sunshine Coast, Australia  
  

**2014**  
  
Oral presentation: Queensland Ornithological Society, Brisbane, Australia  
  
Oral presentation: Australian Society for Parasitology Concepts in Parasitology Workshop, Canberra, Australia.  
  
Taught diagnostic techniques to students in a Parasitology High School Outreach Program at Ulladulla High School, Ulladulla, NSW, Australia  
  

**2013**  
  
Oral presentation: Centre for Integrative Ecology, Deakin University, Geelong, Australia  
  
Poster presentation: Malaria and Related Haemosporidians of Wildlife International Conference, Vilnius, Lithuania  

## Honours and Awards
**2018**
  
Invited to act as guest editor for a [*Tropical Medicine and Infectious Disease* Special Issue](http://www.mdpi.com/journal/tropicalmed/special_issues/Medical_Geography) on disease patterns in a changing environment  
  
**2017**  
  
Invited to act as co-chair for a Wildlife Parasitology session at the Australian Society for Parasitology Conference, Leura, Australia  
  
**2016**  
  
Research article featured on the cover and on the Editor’s Choice list at International Journal for Parasitology  
  
**2014**   
  
1st place oral presentation; Griffith University School of Environment Student Symposium  
  
**2014**  
  
Accepted for competitive placement with travel funds; Australian Society for Parasitology Concepts in Parasitology Workshop, Canberra, Australia  
  
**2012**  
  
Accepted for competitive placement with travel funds; Malaria RCN Student Workshop, Virginia, USA

## Relative to Opportunity
I completed my undergraduate degree (Bachelor of Science; GPA 4.0) in 2009 and completed a Graduate Diploma by Research Methods in 2011 (High Distinction average). I began my PhD in February 2012 and finished in April 2016, delivering a thesis with six published chapters and two published appendices. My PhD work provided new insights into mechanisms driving the distributions of blood parasites in wild birds. I gained a solid theoretical background in multivariate statistics and spatial epidemiology, two fields that I believe currently sit at the nexus of zoonotic disease research.
  
Following my PhD I have devoted much of my postdoctoral work to teaching and mentoring postgraduate research students. This has provided me with a set of leadership and organizational skills that I believe is unique among my peers. It also taught me to be proficient with the time that I have available for research. Since winding down teaching in July 2017, I have published fifteen papers, bringing my total to 25 publications. The quality and significance of this work is reflected by my exemplary publication record in some of the top journals in Disease Ecology. My research has also garnered international recognition. For example, I was invited to present work on new statistical tools for studying parasite niche differentiation at the Australian Society for Parasitology’s 2017 International Conference, where I was also invited to act as co-chair for a wildlife parasitology session. Recently, I have been invited to act as guest editor for a [*Tropical Medicine and Infectious Disease* Special Issue](http://www.mdpi.com/journal/tropicalmed/special_issues/Medical_Geography) on disease patterns in a changing environment. According to *Web of Science* analytics, four of my papers are among the top 10 most cited articles published at UQ SVS / SAFS in the last two years (out of a total of 296 articles published). 

## Referees
* Prof Jennifer Seddon, UQ Gatton Campus; j.seddon1@uq.edu.au 
* Dr Robert Adlard, Queensland Museum; robert.adlard@qm.qld.gov.au
* Dr Sonya Clegg, Oxford University; sonya.clegg@zoo.ox.ac.uk 
* Prof Marcel Klaassen, Deakin University; marcel.klaassen@deakin.edu.au